Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-08-12 paper/snakemajoranas.tex
comment out figures that do not exist
black the notebook

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\columnwidth]{figures/tilted_angle_phase_diagram.pdf}
\caption{A comparison of a straight device (left panels) and a zigzag one (right panels) where the magnetic is rotated.
% E_gap(B, angle, \phi=\pi)
\label{fig:tilted_angle_phase_diagram}}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\columnwidth]{figures/snaking_magnetic_field.pdf}
\caption{
% Fig 4. (d) and (f) with snaking B
\label{fig:snaking_magnetic_field}}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\columnwidth]{figures/bandstructure_of_small_period_zigzag.pdf}
\caption{The effect of increased transparency.
% Like Fig 2. (b) plus horizontal dashed lines indicating the gap of zigzag and straight junctions
\label{fig:bandstructure_of_small_period_zigzag}}
\end{figure}

>>>>

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\columnwidth]{figures/tilted_angle_phase_diagram.pdf}
\caption{A comparison of a straight device (a) and a zigzag one (b) where the magnetic field is rotated.
On the x-axis is the the magnetic field $B$ and on the y-axis is the angle $\theta=\arctan{B_y/B_x}$ in degrees.
The colormaps and the y-axis have a different scale for both panels.
We see that the device with the zigzag geometry is much more resilient against a misaligned magnetic field.
\label{fig:tilted_angle_phase_diagram}}
\end{figure}

@@

% \begin{figure}[!htb]
% \centering
% \includegraphics[width=0.9\columnwidth]{figures/snaking_magnetic_field.pdf}
% \caption{
% % Fig 4. (d) and (f) with snaking B
% \label{fig:snaking_magnetic_field}}
% \end{figure}

% \begin{figure}[!htb]
% \centering
% \includegraphics[width=0.9\columnwidth]{figures/bandstructure_of_small_period_zigzag.pdf}
% \caption{The effect of increased transparency.
% % Like Fig 2. (b) plus horizontal dashed lines indicating the gap of zigzag and straight junctions
% \label{fig:bandstructure_of_small_period_zigzag}}
% \end{figure}
